Confronting preferential sampling in count and occupancy surveys: diagnosis and model-based triage \footnotemark[2]

### 2015-12-01 manuscript/pref_sampling.tex
A few minor changes to ms following Thorson initial comments; Appendix S1 describing model and simulation study in more detail added

\newcommand{\journalnamelc}{British Ecological Society}
\newcommand{\journalabb}{British Ecological Society}
\newcommand{\journalclassshort}{BES}
%%\newcommand{\journalname}{British Ecological Society}
\usepackage{epstopdf}

@@

\item Using simulation, we show that our approach reduces bias resulting from non-random, preferential sampling relative to a traditional species distribution model.  Under strong preferential sampling, biases using traditional species distributions models can be considerable (e.g. 20\%).

@@

\item When animal populations are surveyed using a non-randomized design, we argue that ecologists routinely test and correct for preferential sampling when fitting species distribution models to animal encounter data.

\end{enumerate}

@@

Surveys of unmarked animal populations are often used to estimate abundance and occurrence of animal populations and to predict species distributions, enterprises central to conservation, ecology, and management. For studies of abundance, researchers historically relied on design-based statistical inference \citep[e.g.][]{Cochran1977}, which requires adoption of a pre-defined sampling frame (e.g. using systematic random sampling, stratified random sampling, or some variant thereof).  Designing animal surveys is relatively straightforward in such applications, and unbiased point and variance estimators are available.  Recently, however, there has been a surge in research describing model-based procedures for estimating abundance, density, and occupancy from surveys of unmarked animals, including N-mixture models for repeated point counts \citep{Royle2004a}, occupancy models for presence-absence surveys \citep{MacKenzie2002,JohnsonEtAl2013}, and various model-based formulations for distance-sampling data \citep{HedleyBuckland2004,MillerEtAl2013,JohnsonEtAl2010}.  In such applications, it is common to use habitat or environmental covariates together with spatial effects (e.g. via trend surfaces or spatial random effects) to predict density or distributions across the landscape.  We shall refer to the amalgam of model-based approaches for making spatially explicit inference about animal populations as ``Species distribution models" \citep[SDMs; {\it sensu}][]{ElithLeathwick2009}, even though this term is more often used to refer to animal occurrence than it is to density or abundance.

One of the main advantages of using SDMs advanced in the literature is that one is no longer beholden to predetermined sampling frames, and can potentially use data gathered from non-randomized designs or platforms of opportunity to make inferences about animal populations \citep{JohnsonEtAl2010}.  However,
in a recent paper, \citet{DiggleEtAl2010} emphasized that spatially explicit statistical models can easily provide biased estimates when sampling is nonrandom. The potential for biased estimates arises when sampling locations disproportionately target locations where the response of interest is higher (or lower) than expected given a particular set of explanatory covariates.  In the context of SDMs, this might occur if sampling disproportionately occurs in locations where animals are known to be present or of high abundance, regardless of predictive covariates. For example, if volunteer inventory participants have access to multiple sites with similar covariate values, bias might arise if they consistently choose sites where species are thought or known to be present.  Bias might also arise if surveying effort is higher near bases of operations, and if animal abundance is higher (or lower) near bases of operations than elsewhere in the landscape.

@@

We focus here exclusively on discrete space (areal) models for animal encounter data as these seem to be the dominant form used in design and analysis of animal population surveys, although we note that preferential sampling is likely to affect analyses similarly regardless of the choice of spatial domain.  We suppose that the investigator intending to fit a SDM to animal encounter data breaks their study area up into $S$ survey units (label these $U_1, U_2, \hdots, U_S$), of which $n$ are selected for sampling (call the set of sampled locations $\mathcal{S}$). Each survey unit $i$ is assigned a vector of covariates, ${\bf x}_i$, and an indicator $R_i$ that takes on the value 1.0 if survey unit $i$ is sampled (i.e. if $U_i \in \mathcal{S}$), and is 0 otherwise.  To formulate a ``traditional" SDM, one could then write animal abundance or occurrence as a stochastic realization of a probability mass function $f()$:
\begin{eqnarray}
  \label{eq:process}
  Z_i & \sim & f(g^{-1}(\mu_i)).
\end{eqnarray}
In this example, $Z_i$ denotes the state variable of interest (e.g., occupancy or abundance), $g()$ is a link function (e.g. probit or logit for occupancy, log for count data), and $\mu_i$ is a linear predictor.  In applications described in this paper, we write the linear predictor as
\begin{eqnarray}
\mu_i & = & \beta_0 + {\bf x}_i \boldsymbol{\beta}+\eta_i+\epsilon_i,
 \label{eq:mu}
\end{eqnarray}
where $\beta_0$ is an intercept parameter, ${\bf x}_i$ is a row vector of $m$ predictive covariates associated with site $i$, $\boldsymbol{\beta} = \{ \beta_1, \beta_2, \hdots, \beta_m \}$ is a column vector of $m$ regression parameters, $\eta_i$ is a spatially autocorrelated random effect, and $\epsilon_i$ is Gaussian error.  For occupancy, $f()$ would typically be Bernoulli, while the Poisson or negative binomial are typically choices for analysis of count data; common forms for $\eta_i$ include geostatistical specifications \citep{Cressie1993,DiggleEtAl1998}, Gaussian Markov random fields \citep[e.g. conditionally autoregressive models;][]{RueHeld2005}, or low rank alternatives such as predictive process \citep{BanerjeeEtAl2008,LatimerEtAl2009} or restricted spatial regression models \citep{Reich2006,Hughes2013}.

@@

For the remainder of this treatment, we use bold symbols to denote vector-valued quantities or matrices.  We also use standard bracket notation to denote probability mass and density functions.  For instance $[{\bf Z}]$ denotes the marginal probability mass function for ${\bf Z}$, and  $[{\bf Z}|{\bf Y}]$ represents the conditional distribution of ${\bf Z}$ given ${\bf Y}$.

@@

However, the manner in which effort is ultimately allocated can potentially have profound influence on SDM estimator performance.  With respect to nonrandom sampling, two possible problems seem particularly likely: coarse scale preferential sampling (CSPS), and fine scale preferential sampling (FSPS) (Fig. \ref{fig:pref}).  FSPS arises when the observations taken at a  particular sampling unit are non-random with respect to the density of animals within that sampling unit.  For instance, when allocating line transect survey effort, it may be tempting to place the transect in a manner that targets habitat or landscape features that maximize the number of animals that will be encountered.  Depending upon the interpretation of occupancy, this may or may not be reasonable.  However, if trying to estimate density or abundance, this strategy will clearly lead to positive bias.

@@

@@

Given these limitations, our present task is to generalize PS models to the types of data more typical of SDMs, and to allow the degree of PS to vary across the landscape.  Like \citet{DiggleEtAl2010} and \citet{PatiEtAl2011}, we impose a joint model for the process of interest (animal abundance or occurence) and the locations chosen for sampling. For the process model, we start with Eq. \ref{eq:process} as a general formulation for non-Gaussian data.  We then expand the link-scale expectation from this model
(i.e. Eq. \ref{eq:mu}) as follows:
\begin{eqnarray}
  \mu_i & = & \beta_0 + {\bf x}_i \boldsymbol{\beta}+\delta_i,
\label{eq:mu_aug}
\end{eqnarray}
where $\delta_i$ is a spatially referenced random effect.  Next, we model the binary indicator for sample inclusion using a Bernoulli distribution:
\begin{eqnarray}
 \label{eq:R}
  R_i & \sim & \text{Bernoulli}(h^{-1}(\nu_i)),
\end{eqnarray}
where $h()$ denotes a link function appropriate for binary data (e.g. logit, probit).  We then write the linear predictor for this model as
\begin{eqnarray}
  \label{eq:nu}
  \nu_i & = & \beta_0^* + {\bf x}_i^* \boldsymbol{\beta}^*+\eta_i+{\bf B} \delta_i.
\label{eq:nu}
\end{eqnarray}
 In a similar fashion to the model for the state process, the sampling intensity model has an intercept ($\beta_0^*$), explanatory covariates (${\bf x}_i^*$), fixed effect regression parameters ($\boldsymbol{\beta}^*$), spatially autocorrelated random effects ($\eta_i$ and $\delta_i$), and normally distributed error $\varepsilon_i$.  The predictive covariates ${\bf x}_i$ from Eq. \ref{eq:mu_aug} and ${\bf x}_i^*$ from Eq. \ref{eq:nu} need not be the same (although they can be).  Note also that the  spatially autocorrelated random effect $\delta_i$ is included in both Eqs. \ref{eq:mu_aug} and \ref{eq:nu}, allowing for dependency in the two models, with the matrix {\bf B} describing the strength and type of dependence between the sampling process and underlying density.

@@

To illustrate PS and demonstrate that our proposed model has reasonable performance, we conducted a small simulation experiment.  For each of 100 simulations, we generated abundance of a hypothetical species over a $25 \times 25$ grid as
\begin{eqnarray*}
  N_i \sim \textrm{Poisson}(\mu_i),
\end{eqnarray*}
where $i$ indexes survey unit $i$, and $\mu_i$ is determined according to Eq. \ref{eq:mu_aug}. Abundance was generated as a function of a single spatially autocorrelated landscape covariate, as well as residual spatial autocorrelation ($\delta_i$) and overdispersion (fig. \ref{PS_sims}). Specific details of of data generation procedures are presented in Appendix S1.

@@

We used maximum a posteriori (MAP) estimation to conduct statistical inference. This approach is Bayesian; prior parameter distributions are specified and inference is conducted relative to marginal posterior distributions. However, in contrast to Markov chain Monte Carlo (MCMC) where the posterior is sampled via simulation, the joint posterior is maximized numerically in this case.  We used Template Model Builder \citep[TMB; ][]{KristensenEtAl2015}, interfaced with the R programming environment, to conduct maximization. The TMB software uses a Laplace approximation to integrate out random effects, and a bias correction algorithm \citep{Tierney1989} to obtain abundance estimates that properly account for uncertainty attributable to random effects (\textit{correct, Jim?}).  This approach allowed for a facile implementation and fast computing times, allowing us to conduct simulation and model testing with greater efficiency than would have been possible with MCMC.  In this study, we report the results of 500 simulation replicates.  Further detail on statistical methods are provided in Appendix S1; requisite R and TMB code will be published to a publicly accessible repository upon acceptance, and is also available at \url{https://github.com/NMML/pref_sampling/}.

@@

Estimates of cumulative animal abundance across simulated landscapes were median unbiased for both estimation methods when the sites selected for sampling were independent of animal density, though when $b$ was estimated abundance estimates were more right skewed and had higher variance (fig. \ref{fig:sim_bias}).  Under moderate preferential sampling ($b=1$), the jointly modeling the density and the sampling process (i.e., estimating $b$) led to a median bias of 5\%, while the canonical SDM model had a median bias of 40\%.  Under pathological preferential sampling ($b=5$), both estimation methods were extremely biased, but was even more severe for the naive model ignoring preferential sampling (fig. \ref{sim_bias}).

@@

\begin{table}[ht]
\label{tab:PS}
\caption{Performance of count-based abundance estimators as a function of survey design and estimation model.  Performance measures include proportional relative bias (``Bias"), root mean squared error (``RMSE"), coefficient of variation (``CV"), and 90\% credible interval coverage (``Cov90''; the proportion of simulations where true abundance was between the 5th and 95th percentiles of posterior samples).  Mean values over 400 simulation replicates are presented for spatially balanced sampling (``Balanced"), inverse probability sampling based on covariate values (``Covariate"), and inverse probability sampling based on a priori knowledge of areas of high abundance (``Preferential"). In addition, two different estimation models were applied to each dataset, including a generalized linear model (``GLM''), and a spatial regression model (``RSR'').}
\centering
\begin{tabular}{rrlrrrr}
  \hline
 Design & Model & Bias & RMSE & CV & Cov90 \\
  \hline
Balanced & GLM & 0.00 & 1038 & 0.069 & 0.92 \\
Balanced & RSR & 0.00 & 1034 & 0.057 & 0.90 \\
Covariate & GLM & 0.00 & 1392 & 0.067 & 0.88 \\
Covariate & RSR & 0.00 & 1152 & 0.061 & 0.88 \\
Preferential & GLM & 0.21 & 5807 & 0.060 & 0.24 \\
Preferential & RSR & 0.15 & 3040 & 0.054 & 0.29 \\
   \hline
\end{tabular}
\end{table}

%\begin{figure*}
%\begin{center}
%\includegraphics[width=170mm]{../figures/state_diagram.eps}
%\caption{A depiction of potential inferential obstacles when data from marked animals are %used to address mixed migration strategies. The migratory strategy of an animal will often %be unknown at the time of marking, but observational data may be used to help infer the %proportion of animals subscribing to each strategy, as well as the probability of %migrating for conditional migrants ($\theta_t$).
%behavior} \label{fig:state_diagram}
%\end{center}
%\end{figure*}

>>>>

\newcommand{\journalnamelc}{British Ecological Society}
\newcommand{\journalabb}{British Ecological Society}
\newcommand{\journalclassshort}{BES}
%%\newcommand{\journalname}{British Ecological Society}
\usepackage{epstopdf,comment}

@@

\item Using simulation, we show that under moderate levels of preferential sampling, our modeling approach reduces bias from $\approx$40\% (under a naive species distribution model) to $approx$5\%.

@@

\item When animal population surveys are conducted without a well defined sampling frame, ecologists should recognize the potential for biasing effects of preferential sampling. Joint models, such as those described in this paper, can be used to test and correct for such biases.
\end{enumerate}

@@

Surveys of unmarked animal populations are often used to estimate abundance and occurrence of animal populations and to predict species distributions, enterprises central to conservation, ecology, and management. For studies of abundance, researchers historically relied on design-based statistical inference \citep[e.g.][]{Cochran1977}, which requires adoption of a pre-defined sampling frame (e.g. using systematic random sampling, stratified random sampling, or some variant thereof).  Designing animal surveys is relatively straightforward in such applications, and unbiased point and variance estimators are available.  Recently, however, there has been a surge in research describing model-based procedures for estimating abundance, density, and occupancy from surveys of unmarked animals, including N-mixture and Dail-Madsen models for repeated point counts \citep{Royle2004a,DailMadsen2011}, occupancy models for presence-absence surveys \citep{MacKenzie2002,JohnsonEtAl2013}, and various model-based formulations for distance-sampling data \citep{HedleyBuckland2004,MillerEtAl2013,JohnsonEtAl2010}.  In such applications, it is common to use habitat or environmental covariates together with spatial effects (e.g. via trend surfaces or spatial random effects) to predict density or distributions across the landscape.  We shall refer to the amalgam of model-based approaches for making spatially explicit inference about animal populations as ``Species distribution models" \citep[SDMs; {\it sensu}][]{ElithLeathwick2009}, even though this term is more often used to refer to animal occurrence than it is to density or abundance.

One of the main advantages of using SDMs advanced in the literature is that one is no longer beholden to predetermined sampling frames, and can potentially use data gathered from non-randomized designs or platforms of opportunity to make inferences about animal populations \citep{JohnsonEtAl2010}.  However,
in a recent paper, \citet{DiggleEtAl2010} emphasized that spatially explicit statistical models can easily provide biased estimates when sampling disproportionately targets locations where the response of interest is higher (or lower) than expected given a particular set of explanatory covariates.  In the context of SDMs, this might occur if sampling disproportionately occurs in locations where animals are known to be present or of high abundance, regardless of predictive covariates. For example, if volunteer inventory participants have access to multiple sites with similar covariate values, bias might arise if they consistently choose sites where species are thought or known to be present.  Bias might also arise if surveying effort is higher near bases of operations, and if animal abundance is higher (or lower) near bases of operations than elsewhere in the landscape.

@@

We focus here exclusively on discrete space (areal) models for animal encounter data as these seem to be the dominant form used in design and analysis of animal population surveys, although we note that preferential sampling is likely to affect analyses similarly regardless of the choice of spatial domain.  We suppose that the investigator intending to fit a SDM to animal encounter data breaks their study area up into $S$ survey units (label these $U_1, U_2, \hdots, U_S$), of which $n$ are selected for sampling (call the set of sampled locations $\mathcal{S}$). Each survey unit $i$ is assigned a vector of covariates, ${\bf x}_i$, and an indicator $R_i$ that takes on the value 1.0 if survey unit $i$ is sampled (i.e. if $U_i \in \mathcal{S}$), and is 0 otherwise.  To formulate a ``traditional" SDM, one could then write animal abundance or occurrence as a stochastic realization of a probability mass function $f()$:
\begin{eqnarray}
  \label{eq:process}
  Z_i & \sim & f(g^{-1}(\mu_i)).
\end{eqnarray}
In this example, $Z_i$ denotes the state variable of interest (e.g., occupancy or abundance), $g()$ is a link function (e.g. probit or logit for occupancy, log for count data), and $\mu_i$ is a link-scale intensity value.  In applications described in this paper, we write the intensity as
\begin{eqnarray}
\mu_i & = & \beta_0 + {\bf x}_i \boldsymbol{\beta}+\lambda_i,
 \label{eq:mu}
\end{eqnarray}
where $\beta_0$ is an intercept parameter, ${\bf x}_i$ is a row vector of $m$ predictive covariates associated with site $i$, $\boldsymbol{\beta} = \{ \beta_1, \beta_2, \hdots, \beta_m \}$ is a column vector of $m$ regression parameters, and $\boldsymbol{\lambda}=\{ \lambda_1,\lambda_2,\hdots,\lambda_S \}$ are spatially autocorrelated random effects.  For occupancy, $f()$ would typically be Bernoulli, while the Poisson or negative binomial are typically choices for analysis of count data; common forms for $\lambda_i$ include geostatistical specifications \citep{Cressie1993,DiggleEtAl1998}, Gaussian Markov random fields \citep[e.g. conditionally autoregressive models;][]{RueHeld2005}, or low rank alternatives such as predictive process \citep{BanerjeeEtAl2008,LatimerEtAl2009} or restricted spatial regression models \citep{Reich2006,Hughes2013}.

@@

For the remainder of this treatment, we use bold symbols to denote vector-valued quantities or matrices.  We also use standard bracket notation to denote probability mass and density functions.  For instance $[{\bf Z}]$ denotes the marginal probability mass function for ${\bf Z}$, and  $[{\bf Z}|{\bf Y}]$ represents the conditional distribution of ${\bf Z}$ given ${\bf Y}$.  We use $\boldsymbol{\mu}$ and $\boldsymbol{\nu}$ to denote log-scale abundance and the logit of the probability of sampling, so that $Z_i \sim f(\mu_i)$, and $Y_i \sim f(\nu_i)$.  We use the notation $Z_i$ when describing the state process in general terms, but often switch to the conventional notation $N_i$ when animal abundance is the explicit focus of interest.

@@

However, the manner in which effort is ultimately allocated can potentially have profound influence on SDM estimator performance.  With respect to nonrandom sampling, two possible problems seem particularly likely in discrete spatial domains: coarse scale preferential sampling (CSPS), and fine scale preferential sampling (FSPS) (Fig. \ref{fig:pref}).  FSPS arises when the observations taken at a  particular sampling unit are non-random with respect to the density of animals within that sampling unit.  For instance, when allocating line transect survey effort, it may be tempting to place the transect in a manner that targets habitat or landscape features that maximize the number of animals that will be encountered.  Depending upon the interpretation of occupancy, this may or may not be reasonable.  However, if trying to estimate density or abundance, this strategy will clearly lead to positive bias.

@@

In design-based sampling, unequal sampling intensity is often accommodated via stratification or unequal probability sampling, as with Horvitz-Thompson-like estimators where the probability of inclusion varies by sampling unit \citep{Cochran1977}.  However, in the case of PS, this inclusion probability also depends on the value of the response associated with the sampling unit.  Evidently, any approach to account for PS should also account for the dependence between the state variable of interest and the locations chosen for sampling.

@@

Given these limitations, our present task is to generalize PS models to the types of data more typical of SDMs, and to allow the degree of PS to vary across the landscape.  Like \citet{DiggleEtAl2010} and \citet{PatiEtAl2011}, we impose a joint model for the process of interest (animal abundance or occurence) and the locations chosen for sampling. For the abundance process model, we start with eq. \ref{eq:process} as a general formulation for non-Gaussian data.  We then write the link-scale expectation as in eq. \ref{eq:mu}. 
Next, recalling that $R_i$ is a binary indicator taking on the value 1.0 if survey unit $i$ is selected for sampling, and is 0.0 otherwise, we model $R_i$ using a Bernoulli distribution:
\begin{eqnarray}
 \label{eq:R}
  R_i & \sim & \text{Bernoulli}(h^{-1}(\nu_i)),
\end{eqnarray}
where $h()$ denotes a link function appropriate for binary data (e.g. logit, probit).  We then write the intensity for this model as
\begin{eqnarray}
  \label{eq:nu}
  \nu_i & = & \beta_0^* + {\bf x}_i^* \boldsymbol{\beta}^*+\eta_i+{\bf B} \delta_i.
\label{eq:nu}
\end{eqnarray}
 In a similar fashion to the model for the state process, the sampling intensity model has an intercept ($\beta_0^*$), explanatory covariates (${\bf x}_i^*$), fixed effect regression parameters ($\boldsymbol{\beta}^*$), spatially autocorrelated random effects ($\eta_i$ and $\delta_i$), and normally distributed error $\varepsilon_i$.  The predictive covariates ${\bf x}_i$ from Eq. \ref{eq:mu} and ${\bf x}_i^*$ from Eq. \ref{eq:nu} need not be the same (although they can be).  Note also that the  spatially autocorrelated random effect $\delta_i$ is included in both Eqs. \ref{eq:mu} and \ref{eq:nu}, allowing for dependency in the two models, with the matrix {\bf B} describing the strength and type of dependence between the sampling process and underlying density.  The spatially autocorrelated random effects $\eta_i$ are assumed independent of the abundance process.

@@

To illustrate PS and demonstrate that our proposed model has reasonable performance, we conducted a small simulation experiment.  For each of 100 simulations, we generated abundance of a hypothetical species over a $25 \times 25$ grid as
\begin{eqnarray*}
  N_i \sim \textrm{Poisson}(\mu_i),
\end{eqnarray*}
where $i$ indexes survey unit $i$, and $\mu_i$ is determined according to Eq. \ref{eq:mu}. Abundance was generated as a function of a single spatially autocorrelated landscape covariate, as well as residual spatial autocorrelation ($\delta_i$) and overdispersion (fig. \ref{PS_sims}). Specific details of of data generation procedures are presented in Appendix S1.

@@

We used maximum marginal likelihood estimation to conduct statistical inference. In particular, we used Template Model Builder \citep[TMB; ][]{KristensenEtAl2015}, interfaced with the R programming environment, to conduct maximization. The TMB software uses a Laplace approximation to integrate out random effects, and a bias correction algorithm \citep{TierneyEtAl1989,ThorsonKristensenInPress} to obtain abundance estimates and standard errors that properly account for nonlinear transformations of random effects.  This approach allowed for a facile implementation and fast computing times, allowing us to conduct simulation and model testing with greater efficiency than would have been possible with Bayesian simulation.  In this study, we report the results of 500 simulation replicates.  Further detail on statistical methods are provided in Appendix S1; requisite R and TMB code will be published to a publicly accessible repository upon acceptance, and is also available at \url{https://github.com/NMML/pref_sampling/}.

@@

Estimates of cumulative animal abundance across simulated landscapes were median unbiased for both estimation methods when the sites selected for sampling were independent of animal density, though when $b$ was estimated abundance estimates were more right skewed and had higher variance (fig. \ref{fig:sim_bias}).  Under moderate preferential sampling ($b=1$), the jointly modeling the density and the sampling process (i.e., estimating $b$) led to a median bias of 5\%, while the canonical SDM model had a median bias of 40\%.  Under pathological preferential sampling ($b=5$), both estimation methods were extremely biased, but was even more severe for the naive model ignoring preferential sampling (fig. \ref{fig:sim_bias}).

@@

\begin{comment}
\begin{table}[ht]
\label{tab:PS}
\caption{Performance of count-based abundance estimators as a function of survey design and estimation model.  Performance measures include proportional relative bias (``Bias"), root mean squared error (``RMSE"), coefficient of variation (``CV"), and 90\% credible interval coverage (``Cov90''; the proportion of simulations where true abundance was between the 5th and 95th percentiles of posterior samples).  Mean values over 400 simulation replicates are presented for spatially balanced sampling (``Balanced"), inverse probability sampling based on covariate values (``Covariate"), and inverse probability sampling based on a priori knowledge of areas of high abundance (``Preferential"). In addition, two different estimation models were applied to each dataset, including a generalized linear model (``GLM''), and a spatial regression model (``RSR'').}
\centering
\begin{tabular}{rrlrrrr}
  \hline
 Design & Model & Bias & RMSE & CV & Cov90 \\
  \hline
Balanced & GLM & 0.00 & 1038 & 0.069 & 0.92 \\
Balanced & RSR & 0.00 & 1034 & 0.057 & 0.90 \\
Covariate & GLM & 0.00 & 1392 & 0.067 & 0.88 \\
Covariate & RSR & 0.00 & 1152 & 0.061 & 0.88 \\
Preferential & GLM & 0.21 & 5807 & 0.060 & 0.24 \\
Preferential & RSR & 0.15 & 3040 & 0.054 & 0.29 \\
   \hline
\end{tabular}
\end{table}

\pagebreak
\end{comment}
%\begin{figure*}
%\begin{center}
%\includegraphics[width=170mm]{../figures/state_diagram.eps}
%\caption{A depiction of potential inferential obstacles when data from marked animals are %used to address mixed migration strategies. The migratory strategy of an animal will often %be unknown at the time of marking, but observational data may be used to help infer the %proportion of animals subscribing to each strategy, as well as the probability of %migrating for conditional migrants ($\theta_t$).
%behavior} \label{fig:state_diagram}
%\end{center}
%\end{figure*}
